---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# wcshapes

The goal of wcshapes is to make spatial lagging with country-year but also other panel data easier. 

Goals, basically none implemented yet:

- make a spatial lagger function that plays nicely with sf tibbles
- integrate cshapes data to make spatial lagging with country-year-like data easier
- a country-year spatial lagger solution that respects changes in state-system membership / aka unbalanced panels
- add multiple spatial weight options (see #1)
- add W normalization options (see #2)

## Installation

``` r
library("remotes")
install_github("andybega/wcshapes")
```

NOPE NOT YET: 

You can install the released version of wcshapes from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("wcshapes")
```

## Example

```{r}
library("wcshapes")
library("sf")
library("ggplot2")

data("est_adm1")

est_adm1$x <- as.integer(est_adm1$NAME_1 == "Harju")
w0 <- w_dist_power(st_geometry(est_adm1), alpha = .5)
w1 <- w_dist_power(st_geometry(est_adm1), alpha = 1)
w2 <- w_dist_power(st_geometry(est_adm1), alpha = 2)
est_adm1$x_sl0 <- as.numeric(w0 %*% est_adm1$x)
est_adm1$x_sl1 <- as.numeric(w1 %*% est_adm1$x)
est_adm1$x_sl2 <- as.numeric(w2 %*% est_adm1$x)

plot(est_adm1[, c("x", "x_sl0", "x_sl1", "x_sl2")])
```




